Grounding the interaction: anchoring situated discourse in everyday human-robot interaction

### 2011-07-17 paper_knowledge.tex
Shorten 'article overview' + formatting + missing references

% fixme notes
\usepackage[draft,footnote,marginclue]{fixme}

@@

Daoutis et al.~\cite{Daoutis2009} introduce one of the first complete
architectures for grounded human-robot interaction. They successfully bind
low-level percepts (including view-point independent SIFT based object
recognition) to a high-level knowledge representation and reasoning system via
a dedicated anchoring module. They base their knowledge model directly on the
\textit{ResearchCyc} ontology (including the \textit{MicroTheories} concept),
used in combination with the CycL language. This enables second-order
logic modeling and access to a large common-sense knowledge base.

@@

In the next section we present in depth the so-called {\sc ORO}
(\emph{OpenRobots Ontology} server) knowledge base, a dynamic knowledge
representation system based on Description Logics ontologies and relying on the
\emph{Open World Assumption}. We present it first, along with its objectives,
since it is the knowledge \textit{hub} of the system, used pervasively by other
components.

@@

Section 4 covers in detail the dialogue processing component. The main
algorithms for natural language grounding are described, as well as the
interactions between these component and the knowledge base.

@@

While \emph{knowledge} has no general definition that researchers agree on, for
our own purposes we define knowledge as \emph{information interpreted in the
cultural and social context of the robot}, where information is a
\emph{statement} or an \emph{assertion} about the world\footnote{In this paper,
statements are always triples \texttt{<subject, predicate, object>}, following
the Description Logics formalism.}. In practical terms, knowledge is made of
statements that are \emph{contextualized}, if possible \emph{synthesized}, and
\emph{limited} to a domain of validity.

@@

Our common sense ontology is closely aligned with the open-source
OpenCyc\footnote{\url{http://www.opencyc.org}} upper ontology.
OpenCyc defines a large taxonomy of concepts and semantic
relationships between concepts that are used in several other projects
(\textsc{WordNet, DBpedia}). This potentially eases the exchange and addition
of knowledge from these other sources. Moreover, it also enables knowledge
exchange with other robots (for instance, the works previously mentioned by
Daoutis and Tenorth rely on the same Cyc concepts\fixme{Give
examples}).

@@

While no examples involving questions have been detailed, \emph{W-} questions
and \emph{yes/no} questions can be processed in a similar way by
\textsc{Dialogs}. For instance, a question like ``What is on the table?''
is grounded (to extract the relation \concept{isOn} and to find what \emph{table}
refers to) and transformed into the following kind of query: {\tt find ?var
[\stmt{?var isOn table1}]}.  Answers are converted back to a full sentence
by the \emph{verbalization} module, and uttered to the human.

@@

\subsubsection{Explicit disambiguation through verbal interaction and gestures}
\begin{figure}[!ht]
  \centering
  \subfigure[]
  {\includegraphics[width=0.9\linewidth]{images/inTheBox1.jpg}\label{a}}
  \subfigure[]
  {\includegraphics[width=0.9\linewidth]{images/inTheBox2.jpg}\label{b}}
\caption{(a) Jerry asks Jido for the content of the box and (b) points at it.}
  \label{fig|pointing}
\end{figure}

>>>>

@@

Daoutis et al.~\cite{Daoutis2009} introduce one of the first complete
architectures for grounded human-robot interaction. They successfully bind
low-level percepts (including view-point independent SIFT based object
recognition) to a high-level knowledge representation and reasoning system via
a dedicated anchoring module. They base their knowledge model directly on the
\textit{ResearchCyc} ontology (including the \textit{MicroTheories} concept),
used in combination with the {\sc CycL} language. This enables second-order
logic modeling and access to a large common-sense knowledge base.

@@

In the next section we present the {\sc ORO}
(\emph{OpenRobots Ontology} server) knowledge base. We present it first, along with its objectives,
since it is the knowledge \textit{hub} of the system, used pervasively by other
components.

@@

Section 4 covers in detail the dialogue processing component.

@@

While \emph{knowledge} has no general definition that researchers agree on, for
our own purposes we define knowledge as \emph{information interpreted in the
cultural and social context of the robot}, where information is a
\emph{statement} or an \emph{assertion} about the world\footnote{In this paper,
statements are always triples \stmt{subject predicate object}, \ie binary
relations between entities.}. In practical terms, knowledge is made of
statements that are \emph{contextualized}, if possible \emph{synthesized}, and
\emph{limited} to a domain of validity.

@@

Our common sense ontology is closely aligned with the open-source
OpenCyc\footnote{\url{http://www.opencyc.org}} upper ontology.
OpenCyc defines a large taxonomy of concepts and semantic
relationships between concepts that are used in several other projects
(\textsc{WordNet, DBpedia}). This potentially eases the exchange and addition
of knowledge from these other sources. Moreover, it also enables knowledge
exchange with other robots (for instance, the works previously mentioned by
Daoutis and Tenorth rely on the same Cyc concepts).

@@

While no examples involving questions have been detailed, \emph{W-} questions
and \emph{yes/no} questions can be processed in a similar way by
\textsc{Dialogs}. For instance, a question like ``What is on the table?''
is grounded (to extract the relation \concept{isOn} and to find what \emph{table}
refers to) and transformed into the following kind of query: \concept{find ?var
[\stmt{?var isOn table1}]}.  Answers are converted back to a full sentence
by the \emph{verbalization} module, and uttered to the human.

@@

\subsubsection{Explicit disambiguation through verbal interaction and gestures}
\label{disamb-gestures}

\begin{figure}[!ht]
  \centering
  \subfigure[]
  {\includegraphics[width=0.9\linewidth]{images/inTheBox1.jpg}\label{a}}
  \subfigure[]
  {\includegraphics[width=0.9\linewidth]{images/inTheBox2.jpg}\label{b}}
\caption{(a) Jerry asks Jido for the content of the box and (b) points at it.}
  \label{fig|pointing}
\end{figure}
